\Title

### 2015-11-02 manuscript.tex
More about the data set separation for CV

Bott's method requires the same number of observed data ($N$)
and model parameters ($M$).
Limited ways to separate the training and testing data sets.
Data and model must be on a regular grid.
Cannot randomly separate.
Use a dense data grid.
Take for the training set a sub grid with double the original grid spacing.
Every other point is included in the testing data set.
The testing data set will have more points than training data set.
One can generate observed data on a grid with half of the desired grid spacing.
This is easy for data generated from spherical harmonic models.

>>>>

The separation of the training and testing data sets is commonly done by taking
random samples from the full data set.
However, we cannot perform the separation in this way because
Bott's method requires data on a regular grid as well as having model elements
directly below each data point.
Thus, we take as our training set the points from the observed data grid that
fall on a similar grid but with twice the grid spacing
(see Fig.~\ref{fig:grid_separation}).
\todo{Include fig from seminar}
All other points from the original data grid
make up the testing data set.
This separation will lead to
a testing data set with more points than the training data set.
A way to balance this loss of data in the inversion
is to generate a data grid with half of the desired grid spacing,
either through interpolation
or from a spherical harmonic model.

\begin{figure}
    \centering
    %\includegraphics[width=\columnwidth]{figures/paper/sam-gravity-data}
    \caption{This is a figure caption.}
    \label{fig:grid_separation}
\end{figure}
